---
title: "Assignements network"
author: "Pedro Jordano"
date: "enero 19, 2015"
output: html_document
---
   
[**Jordano's lab R Figures Catalog**](https://github.com/PJordano-Lab/R-figures)

```{r setup, include=FALSE}
# Do not remove this chunk #
library(knitr)
opts_chunk$set(fig.path = gsub("\\.Rmd", "", paste0("../figures/", current_input(), "-")),
               fig.align='center')

```


## Tree assignements example 

Suppose we have a matrix (an adjacency matrix) with the number of tree genotypes resulting assigned to different populations within a region (e.g., a metapopulation). This plots the network of tree assignements so that we can better assess the connectivity patterns among them.   
   
      
#### Data input

We use an adjacency matrix among 11 populations/stands obtained from immigrant/emigrant Bayesian estimates obtained with BayesAss (Rannala and Mountain 1997). Other network reprersentations of population connectivity can be obtained with the `gstudio` package (see Dyer and Nason 2004).

In this adjacency matrix we coded the number of immigrant/emigrant genotypes for tree populations `A`, `B`, `C`, and `D`, located within a given area. `OUT` represents the emigrant/immigrant genotypes to/from populations outside the area:    

```{r matrix}
require(igraph) # This loads the igraph package

# Direct input of adjacency matrix
#
# From: ->To:   | A  | B  | C  | D  | OUT
# --------------|----|----|----|----|----
# A             |110 |  0 | 4  | 0  | 7
# B             |  3 |  4 | 0  | 0  | 7
# C             | 29 | 15 | 10 | 18 | 3
# D             | 33 |  0 | 1  | 0  | 0
# OUT           |  4 |  5 | 2  | 1  | 16

myobject = data.frame(matrix( 
    c(110, 0, 4, 0, 7,
      3, 4, 0, 0, 7,
      29, 15, 10, 18, 3,
      33, 0, 1, 0, 0,
      4, 5, 2, 1, 16),  
    nrow=5,              
    ncol=5,              
    byrow = TRUE))      
colnames(myobject)<-row.names(myobject)<- c("A","B","C","D","OUT")
```
   
   
Note that it is a square, asymmetric matrix, so that entries represent the number of immigrants from `row`population to `column`population. The diagonal cells are the number of genotypes actually in population `i`, inferred to come from that same population (i.e., originating from local, _in situ_ dispersal events).  
  
  
#### Plotting the network

```{r plot, fig.height= 8, fig.width= 6}
m= as.matrix(myobject)              # coerces the data set as a matrix
g= graph.adjacency(m, mode="directed", 
                   weighted=T, diag=T)        # this will create
                                              # an 'igraph object'
# Plotting the directed adjacency matrix.
plot.igraph(g, vertex.label= V(g)$name, 
            layout=layout.fruchterman.reingold,
            vertex.label.color="black",
            vertex.label.cex=0.8,
        	edge.color="black",
			edge.width=E(g)$weight/10,
			edge.arrow.size=0.8,
			edge.curved=TRUE)
```


#### References

1. Rannala, B. & Mountain, J. (1997). Detecting immigration by using multilocus genotypes. _Proceed. Natl. Acad. Sci. USA_, **94**: 9197–9201.

2. Dyer, R.J. & Nason, J.D. (2004). Population Graphs: the graph theoretic shape of genetic structure. _Molecular Ecology_, **13**: 1713–1727.
    
----------------------------------
```{r}
sessionInfo()
```

----------------------------------
