---
title: "ChromosomeNetwork"
author: "amesclir"
date: "03/03/2015"
output: html_document
---
Getting the package igraph.
```{r}
require(igraph)
```

Reading the data set.

```{r}
mydata <- read.csv("ChromosomeNetwork.csv")
mydata
```

Getting network igraph format and plottig the first graph.
Note: By doing this log(E(g)$GR+10)), the conectiones between circles look clearer.

```{r}
g<-graph.data.frame(mydata, directed=F)
g
V(g)
E(g)
E(g)$GR
V(g)$label.cex = 0.3
plot(g, layout = layout.auto, edge.width=(E(g)$GR)/10)

```

Now we are going to try to put the chromosome number information.
1. Putting chromosome number information in the vertex (it is not really necessary right now)
2. Putting gray scale in the vertex

```{r}
g2 <- g
V(g2)$X2n <- c(68, 66, 66, 66, 65, 68, 62, 66, 66, 66, 68, 66, 67, 64, 64, 62, 67, 66, 64, 65, 67)
V(g2)$color <- c("white", "gray60", "gray60","gray60","gray40","gray80","black","gray60","gray60","gray60", "white", "gray60", "gray80", "gray20","gray20","black", "gray80","gray60","gray20","gray40","gray80")   
V(g2)$label.cex = 0.3
plot(g2, layout = layout.auto, edge.width=(E(g)$GR)/10)
legend("bottomright", c("62","64","65", "66", "67", "68"),pch=c(16,16,16,16,16,1),col=c("black", "gray20", "gray40", "gray60", "gray80", "black"),cex=0.7)

```

Now the chromosome number in the vertices.

```{r}
g3 <- g
V(g3)$name <- as.character(V(g2)$X2n)
V(g3)$color <- rep("white", 21)
V(g3)$label.cex = 0.5
plot(g3, edge.width=(E(g)$GR)/10)

```

Final important chunk
```{r}
sessionInfo()
```

