---
title: "Plotting effectiveness landscapes"
author: "Pedro Jordano"
date: "enero 28, 2015"
output: html_document
---

### Code for plotting the effectiveness landscape of mutualisms adding isolines of equal effectiveness values.

Effectiveness landscapes are the two-dimensional representation of the possible combinations of the quantity and the quality of mutualistic services (seed dispersal, pollination) and with elevational contours representing isoclines of effectiveness. These representations can be 2D bivariate plots of multiplicative effects of any of the seed dispersal (SDE) or pollination (PE) effectiveness components.  

This is a repository of code used to produce these plots.  

The script plots effectiveness landscapes as described in:  

Schupp, E. W., Jordano, P. and Gómez, J.M. 2010. Seed dispersal effectiveness revisited: a conceptual review. New Phytologist, 188: 333-353.  

For additional details please visit the [web page here](http://pedroj.github.com/effectiveness/). Or try [my GitHub repository](https://github.com/pedroj/effectiveness).  

Below is the code for the `effectiveness` function. You can source the code directly with:

```{r sourcing, echo=TRUE, eval=FALSE}
require(downloader)
#
# Sourcing the effectiveness function code from GitHub.
link = "https://raw.githubusercontent.com/pedroj/effectiveness/master/effectiveness.R"
file = "effectiveness.R"
if(!file.exists(file)) download(link, file, mode = "wb")
source(file)
```


```{r effectiveness_function, echo=T}
#---------------------------------------------------------------------------
# effectiveness
# Function to plot effectiveness landscapes.
#---------------------------------------------------------------------------
# autoisolines: Code for automatically plotting isolines of
# effectiveness landscapes.
# Based on code for plotting effectiveness landscapes by Pedro 
# Jordano and code for automatic calculation of isolines 
# by Bernardo Santos.
# 3 December 2013. UNESP, Rio Claro, Brazil. Pedro Jordano.
#---------------------------------------------------------------------------
## First version 12 Jan 2009. Revised 3 December 2013.
## New revision 23 January 2015.
#---------------------------------------------------------------------------
# Options:
#   q1, the "quantitative component", to plot on the X axis. 
#   q2, the "qualitative component", to plot on the Y axis.
#   group=NA, a grouping variable to set point shapes (e.g., family).
#   label= NA, a label for the individual points (e.g., spcies acronym).
#   nlines=10, specify the number of isolines.
#   myxlab= "QtComp", optional label for axis X.
#   myylab= "QltComp", optional label for axis Y.
# 
# Example:
# effectiveness(sde$visits, sde$eff_per_vis, sde$group, sde$animal, 10, 
#               myxlab= "No. visits/10h", 
#               myylab="Effectiveness/vis (No. fruits handled)")
# effectiveness(cgla$totvis, cgla$totbic, cgla$fam, cgla$code, 15, 
#               myxlab= "Total no. visits", 
#               myylab="No. fruits pecked/vis")
#---------------------------------------------------------------------------
#
effectiveness<- function(q1, q2, group=NA, label= NA, nlines=10,
                        myxlab= "QtComp", myylab= "QltComp")    {
    # q1 is the component to plot on X axis
    # q2 is the component to plot on Y axis
    # group is a group label
    # label is a taxa label
    require(devtools)
    require(ggplot2)
    #
    d<-as.data.frame(cbind(q1, q2, group, label))
    names(d)
    nlines <- nlines+1 # number of isolines wanted
    # slope of a straight line linking (left,bottom) to (right,above) 
    # corners of the graphic
    alfa <- max(d$q2)/max(d$q1)
    # sequence of (nlines) regular spaced x values for the isoclines
    xval <- seq(0, max(d$q1), 
        length.out=(nlines+1))[2:(nlines+1)] 
    isoc <- (xval*xval*alfa) # values of the isoclines
    vis1<-seq(0, max(d$q1), length.out= 1000)
    #
    pp<- as.data.frame(vis1) # Build dataset for within loop plot.
    for(i in 1:nlines)
    {
        pp<- cbind(pp, isoc[i]/vis1)
    }    
    # Main plot ------------------------------------------------------------
    # mytheme_bw.R
    devtools::source_gist("https://gist.github.com/b843fbafa3af8f408972")
    #
    p1<- ggplot(d, aes(x=q1, y=q2)) + 
        geom_point(shape= group, size=5) +
        geom_text(size= 4, label= label, hjust= 0.5, vjust= 1.9) +
        mytheme_bw()
    # Adding isolines ------------------------------------------------------
    labelx<- rep(0.8*max(q1), nlines)
    labely<- as.vector(t(pp[800,1:nlines+1]))
    
    for(i in 1:nlines+1){ 
         p1= p1 + geom_line(aes(x, y), 
            data= data.frame(x= pp$vis1, y= pp[,i]), 
            col="blue", size = 0.25, alpha= 0.6) + 
            ylim(0, max(q2)) +
            xlab(paste(myxlab)) + 
            ylab(paste(myylab))
    }
    p1 + annotate("text", x= labelx, y= labely,
        label=paste("QC= ", round(isoc,1)), 
        size=4, colour="red", hjust=0) 
}
#---------------------------------------------------------------------------
```


### Example

```{r example, message=FALSE, warning=FALSE, fig.height= 6,fig.width=8}
require(downloader)
#
# PJ example. Based on a dataset of Prunus mahaleb frugivores.
# Get the data from my GitHub repository.
link = "https://raw.githubusercontent.com/pedroj/effectiveness/master/data.txt"
file = "data.txt"
if(!file.exists(file)) download(link, file, mode = "wb")
M <- read.table(file, sep = "\t", dec = ".", 
                header = TRUE, na.strings="NA")

# Run the function.
effectiveness(M$visits, M$eff_per_vis, M$group, M$animal, 10, 
                myxlab= "No. visits/10h", 
                myylab="Effectiveness/vis (No. fruits handled)")
```

----------------------------------
```{r}
sessionInfo()
```

----------------------------------


