---
title: "Dispersal kernels"
author: "Pedro Jordano"
date: "febrero 19, 2015"
output: html_document
---


[**Jordano's lab R Figures Catalog**](https://github.com/PJordano-Lab/R-figures)

```{r setup, include=FALSE}
# Do not remove this chunk #
library(knitr)
opts_chunk$set(fig.path = gsub("\\.Rmd", "", paste0("../figures/", current_input(), "-")),
               fig.align='center')

```


### Code for plotting dispersal kernels

Dispersal kernels depict frequency distributions of dispersal distance, the Euclidean distance between ‘start’ and ‘end’ points of a dispersal event.  

The function raw code is [available here](https://github.com/pedroj/dispkernels/raw/master/functions/mykernel.R).    
   
The functions plots the `pdf` for the kernel and `n= 100` bootstrapped distributions by randomply resampling the distance vector.   

Input in function call is the data vector of distances and an upper limit for estimating the kernel.   
Possible startup values:    
`dd`: data vector of distances.    
`up`: upper distance limit for estimating the kernel.    
`prob`: probability Y axis [TRUE].     
`bw`: the smoothing bandwidth to be used for the kernel envelope.     
`h`: the bin width.    



### Example

```{r plot, message=FALSE, warning=FALSE, fig.height= 6,fig.width=8}
# Sourcing the kernel function code from GitHub.
require(downloader)
link = "https://raw.githubusercontent.com/pedroj/dispkernels/master/functions/mykernel.R"
file = "./mykernel.R"
if(!file.exists(file)) download(link, file, mode = "wb")
source(file)

ddTF<- rweibull(1000, shape= 1, scale = 3.5) # Weibull distrib.
ddGC<- as.data.frame(rweibull(1000, shape= 0.7, scale = 3.0)) # Weibull distrib.

mykernel(ddTF, bw= 0.5, h= 0.25) # Extract the distances vector

# An example with ggplot2
# Plot randomized kernel with specific mean and SD values.
#
library(ggplot2)

ggplot(ddGC, aes(x=ddGC[,1])) +
    theme_bw() +
    geom_histogram(aes(y = ..density..), 
                   binwidth=density(ddGC[,1])$bw,
                   fill="blue", alpha = 0.5) +
    geom_density(fill="red", alpha = 0.2) +
#    theme_bw() +
    geom_rug(sides="b", color="red") +
    xlab('Distance (m)') +
    ylab('Probability')

# Cleanup
file.remove("./Spatial/mykernel.R")
```

----------------------------------
```{r}
sessionInfo()
```

----------------------------------
